HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-17 paper/main.tex
sss

Let $\Correct(s,t)$ be the number of atomic units in $s$ marked as Green relative to $t$ plus
the number of structural units in $s$ marked as Adequate relative to $t$.
Let $\Partial(s,t)$ be the number of atomic units in $s$ marked as Orange relative
to $t$. Then HUME's composite score is:

@@

In HMEANT, the alignment between the (source and candidate) structures is a key
part of the manual annotation. If the alignment cannot be created, the candidate
translation is heavily penalized in score.
Previous experiments with HMEANT
\parcite{bojar:wu:ssst:2012,chuchunkov-tarelkin-galinskaya:2014:SSST-8} have
suggested that modifications to the two structures are desirable and appropriate
at the alignment stage, to avoid unduly penalization due to spurious diverges in
the structures.
The same issue was observed by HMEANT authors themselves \parcite{XXXcite}
\XXX{cite this: http://repository.ust.hk/ir/Record/1783.1-66107}: the
inter-annotator agreement on SRL dropped from 90\% to 61\% 
when the two aligned structures were from two different annotators.

HUME uses only automatic (word-level) alignment, and it's only purpose is to
make the annotation process easier. The alignment is indicative only and the
user is expected to mentally correct the alignment as needed.

@@

This requires us to employ bilingual annotators, but has the benefit of avoiding
the reference translation. It is known that the reference translations are not
always literal enough and the MT output semantics can be composed differently
than the semantics of the reference. While this is in principle not a problem
for HUME (the whole sentence can be labelled as ``Green''), it prevents learning
any fine-grained information about the MT output.

Perhaps even more importantly,
the reference translations were often not created by translating the source
sentences. In some cases, the manual translation was reversed, or both the
``source'' and ``reference'' are actually independent translations from a third
language. The ``reference'' can thus easily contain more information than the
``source''.

>>>>

Let $\Correct(s,t)$ be the number of atomic units in $s$ marked as Green relative to $t$ plus
the number of structural units in $s$ marked as Adequate relative to $t$.
Let $\Partial(s,t)$ be the number of atomic units in $s$ marked as Orange relative
to $t$. Let $\Units(s)$ be the total number of units marked with any of the five labels.
Then HUME's composite score is:

@@

In HMEANT, the alignment between the (source and candidate) structures is a key
part of the manual annotation. If the alignment cannot be created, the candidate
translation is heavily penalized in score.
Previous experiments with HMEANT
\parcite{bojar:wu:ssst:2012,chuchunkov-tarelkin-galinskaya:2014:SSST-8} have
suggested that modifications to the two structures are desirable and appropriate
at the alignment stage, to avoid unduly penalization due to spurious diverges in
the structures.\oa{I didn't understand this}
The same issue was observed by HMEANT authors themselves \parcite{XXXcite}
\XXX{cite this: http://repository.ust.hk/ir/Record/1783.1-66107}: the 
inter-annotator agreement on SRL dropped from 90\% to 61\% 
when the two aligned structures were from two different annotators.

HUME uses only automatic (word-level) alignment, which only serves as a cue for directing
the attention of the annotators.
The user is expected to mentally correct the alignment as needed.

@@

This requires us to employ bilingual annotators, but has the benefit of avoiding
the reference translation. It is known that the reference translations are not
always literal enough and the MT output semantics can be composed differently
than the semantics of the reference. While HUME avoids this problem,
imposing a structure only on the source does prevent any fine-grained semantic
analysis of the translation.

Perhaps more importantly, references are often not created by translating the source
sentences. In some cases, the manual translation was reversed\oa{what does that mean?},
and in others the ``source'' and ``reference'' are actually independent translations
from a third language. ``References'' can thus easily contain information
that does not appear in the ``source''.
